---
title: "estimators_sandbox_052421"
author: "Igor Geyn"
date: "5/24/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Setting up data

```{r}

### quickest way is to install the package
### it comes with data

# devtools
library(devtools)
devtools::install_github("igorgeyn/benchtestr/benchtestr")

# remotes -- is lighter!
install.packages('remotes')
remove.packages('benchtestr')
remotes::install_github("igorgeyn/benchtestr/benchtestr") # gotta check on these errors at some point
load('nsw_dehejia_wahba')

# having issues with package installation

### using filepaths

# from laptop (IG)
load('C:/Users/Igor Geyn/Desktop/grad school/coursework/SPRING 21/benchtestr/benchtestr/data/nsw_dehejia_wahba.rda')
load('C:/Users/Igor Geyn/Desktop/grad school/coursework/SPRING 21/benchtestr/benchtestr/data/psid_controls_dw.rda')
load('C:/Users/Igor Geyn/Desktop/grad school/coursework/SPRING 21/benchtestr/benchtestr/data/cps_controls_dw.rda')

# from desktop (IG)

load('C:/Users/Igor/Desktop/grad school/coursework/SP21/200C/package/benchmarkr/benchtestr/data/lalonde.rda')

load('C:/Users/Igor/Desktop/grad school/coursework/SP21/200C/package/benchmarkr/benchtestr/data/nsw_dehejia_wahba.rda')
load('C:/Users/Igor/Desktop/grad school/coursework/SP21/200C/package/benchmarkr/benchtestr/data/psid_controls_dw.rda')
load('C:/Users/Igor/Desktop/grad school/coursework/SP21/200C/package/benchmarkr/benchtestr/data/cps_controls_dw.rda')



data()
data(psid_controls_dw)
head(cps_controls_dw)

data(ajps)

```

## Trying out estimators

### 'Naive' DIM

The goal here is just to create a pseudo control group from the PSID controls dataset that can be used to create a benchmark DIM. Should compare this DIM against the DIM obtained from the initial dataset.

```{r}

head(estimator_baseline)

### grab the existing DIM estimator

baseline_dim_estimator <- function(df_exp, df_base, treatment, outcome) {
  require('dplyr')
  # results_df <<- as.data.frame(matrix())
  treatment_sym <- sym(treatment)
  outcome_sym <- sym(outcome)
  estimator_exp <<- df_exp %>%
    group_by(!!treatment_sym) %>%
    summarise(avg_earnings = mean(!!outcome_sym),
              earnings_var = var(!!outcome_sym),
              count = n())
  
    estimator_full <<- df_base %>%
    group_by(!!treatment_sym) %>%
    summarise(avg_earnings = mean(!!outcome_sym),
              earnings_var = var(!!outcome_sym),
              count = n())
  
  estimator_bench_cntrl <<- df_base %>% 
    filter(!!treatment_sym == 0) %>% 
    group_by(!!treatment_sym) %>% 
    summarise(avg_earnings = mean(!!outcome_sym),
              earnings_var = var(!!outcome_sym),
              count = n())

  estimate_full <<- estimator_full$avg_earnings[2] - estimator_full$avg_earnings[1]
  se_full <<- sqrt((estimator_full$earnings_var[1]/estimator_full$count[1])+
                         (estimator_full$earnings_var[2]/estimator_full$count[2]))
  
  
  estimate_benchmark_cntrl <<- estimator_full$avg_earnings[2] - estimator_bench_cntrl[1]
  se_benchmark_cntrl <<- sqrt((estimator_full$earnings_var[2]/estimator_full$count[2])+
                                (estimator_bench_cntrl$earnings_var[1])/estimator_bench_cntrl$count[1])
  
  # doesn't work -- full version
  # estimate_benchmark <<- estimator_full$avg_earnings[2] - estimator_full$avg_earnings[1]
  
  results_exp <<- 
    as.data.frame(cbind(as.character('experimental/baseline'), as.double(estimate_full), as.double(se_full))) %>% 
    rename(data = V1, estimate = estimate_full, se = se_full)
    # %>% rename(data = V1)
  ## need to figure out why the var names are coming out weird
  results_bench <<- 
    as.data.frame(cbind(as.character('benchmark'), as.double(estimate_benchmark_cntrl), as.double(se_benchmark_cntrl))) # %>%
    rename(data = '\benchmark\'', estimate = estimate_benchmark_cntrl, se = se_benchmark_cntrl)
  
  ## pending solution to above issue
  ## binding manually for now
  results_df_out <<- rbind(results_exp, results_bench)
  
}

# this works!
baseline_dim_estimator(df_exp = nsw_dehejia_wahba, df_base = psid_controls_dw,
                       treatment = 'treat', outcome = 're78')

### manual binding

results_bench$"benchmark"

class(results_bench)
# huzzah!! this works now
# having some problems with the quoted benchmark var [RESOLVED]
results_bench <- results_bench %>% 
  rename(data = ("\"benchmark\""),
         estimate = treat,
         se = se_benchmark_cntrl)
# # trying another way [DEFUNCT]
# var_names = c('data', 'estimate', 'se')
# results_bench %>% make.names(var_names)

results_df_out <<- rbind(results_exp, results_bench)

#### #
##### sandbox
#####

benchmark_dim_estimator <- function(df_base, treatment, outcome) {
  require('dplyr')
  benchmark_results_df <<- as.data.frame(matrix()) # eventually get rid of this
  treatment_sym <- sym(treatment)
  outcome_sym <- sym(outcome)
  estimator_benchmark <<- df_base %>%
    group_by(!!treatment_sym) %>%
    summarise(avg_earnings = mean(!!outcome_sym),
              earnings_var = var(!!outcome_sym),
              count = n())
  
  estimate_benchmark <<- estimator_benchmark$avg_earnings[2] - estimator_benchmark$avg_earnings[1]
  se_benchmark <<- sqrt((estimator_benchmark$earnings_var[1]/estimator_benchmark$count[1])+
                         (estimator_benchmark$earnings_var[2]/estimator_benchmark$count[2]))
  
  benchmark_results_df <<- cbind('benchmark', estimate_benchmark, se_benchmark)
  results_df <<- rbind(results_df,benchmark_results_df)
}

benchmark_dim_estimator(df_base = psid_controls_dw %>% filter(treat == 0),
                        treatment = 'treat',
                        outcome = 're78')

```
### DIM estimator 

```{r}
dim_estimator = function(df_exp, df_base, treatment, outcome){
  require(estimatr)
  
  # Select only the treatment and outcome variables
  df_exp = df_exp %>% dplyr::select(matches(paste(treatment, outcome, sep = "|"))) %>% mutate_at(treatment, as.numeric)
  df_base = df_base %>% dplyr::select(matches(paste(treatment, outcome, sep = "|"))) %>% mutate_at(treatment, as.numeric)
  
  # Estimate three different ways of DIM
  dim_exp = difference_in_means(as.formula(paste(outcome, "~", treatment)), data = df_exp) %>%
    tidy() %>% mutate(nature = "experimental")
  if(mean(df_base["treat"][,1]) > 0){
    dim_base = difference_in_means(as.formula(paste(outcome, "~", treatment)), data = df_base) %>%
    tidy() %>% mutate(nature = "base")
  } else {
    dim_base = dim_exp
  }
  dim_bench = difference_in_means(as.formula(paste(outcome, "~", treatment)), data = rbind(df_exp, df_base)) %>%
    tidy() %>% mutate(nature = "benched")
  
  return(rbind(dim_exp, dim_base, dim_bench) %>% unique() %>% dplyr::select(nature, everything()))
}
dim_estimator(df_exp = nsw_dehejia_wahba, df_base = psid_controls_dw,
              treatment = 'treat', outcome = 're78')
```

### LM estimator

```{r}
lm_estimator = function(df_exp, df_base, treatment, outcome, delete_vars = "id|source"){
  require(estimatr)
  
  # Avoid problems with logical treatment variables
  df_exp = df_exp %>% mutate_at(treatment, as.numeric)
  df_base = df_base %>% mutate_at(treatment, as.numeric)
  
  # Find out the control variables
  controls = names(df_exp)
  controls = controls[!grepl(delete_vars, controls) & controls != treatment & controls != outcome]
  controls = paste(controls, collapse = " + ")
  
  # Three different ways of LM estimators
  lm_exp = lm_robust(as.formula(paste(outcome, "~", treatment, "+", controls)), data = df_exp) %>%
    tidy() %>% mutate(nature = "experimental")
  if(mean(df_base["treat"][,1]) > 0){
    lm_base = lm_robust(as.formula(paste(outcome, "~", treatment, "+", controls)), data = df_base) %>%
      tidy() %>% mutate(nature = "base")
  } else {
    lm_base = lm_exp
  }
  lm_bench = lm_robust(as.formula(paste(outcome, "~", treatment, "+", controls)), 
                       data = rbind(df_exp %>% dplyr::select(matches(paste(treatment, outcome, gsub(" \\+ ", "|", controls), sep = "|"))), 
                                    df_base %>% dplyr::select(matches(paste(treatment, outcome, gsub(" \\+ ", "|", controls), sep = "|"))))) %>%
    tidy() %>% mutate(nature = "benched")
  
  return(rbind(lm_exp, lm_base, lm_bench) %>% unique() %>% dplyr::select(nature, everything()) %>% 
           filter(term == "treat") %>% mutate(control = controls))
}
lm_estimator(df_exp = nsw_dehejia_wahba, df_base = psid_controls_dw,
             treatment = 'treat', outcome = 're78')
```

### IV estimator

```{r}
iv_estimator = function(df_exp, df_base, treatment, outcome, delete_vars = "id|source"){
  require(estimatr)
  
  # Avoid problems with logical treatment variables
  df_exp = df_exp %>% mutate_at(treatment, as.numeric) %>% dplyr::select(!matches(delete_vars))
  df_base = df_base %>% mutate_at(treatment, as.numeric) %>% dplyr::select(!matches(delete_vars))
  
  # Find out the instrumental variable
  iv_var = cor(df_exp) %>% as.data.frame() %>% mutate(term = colnames(.)) %>% 
    dplyr::select(matches(paste("term", treatment, outcome, sep = "|"))) %>% 
    filter(term != treatment & term != outcome) %>%
    mutate(value = abs(!!sym(treatment)) - abs(!!sym(outcome))) %>%
    arrange(desc(value))
  iv_var = iv_var$term[1]
  
  # Find out the control variables
  controls = names(df_exp)
  controls = controls[!grepl(delete_vars, controls) & controls != treatment & controls != outcome & controls != iv_var]
  controls = paste(controls, collapse = " + ")
  
  # Three different ways of IV estimators
  iv_exp = iv_robust(as.formula(paste(outcome, "~", treatment, "+", controls, "|", iv_var, "+", controls)), data = df_exp) %>%
    tidy() %>% mutate(nature = "experimental")
  if(mean(df_base["treat"][,1]) > 0){
    iv_base = iv_robust(as.formula(paste(outcome, "~", treatment, "+", controls, "|", iv_var, "+", controls)), data = df_base) %>%
     tidy() %>% mutate(nature = "base")
  } else {
    iv_base = iv_exp
  }
  iv_bench = iv_robust(as.formula(paste(outcome, "~", treatment, "+", controls, "|", iv_var, "+", controls)), 
                       data = rbind(df_exp, df_base)) %>%
    tidy() %>% mutate(nature = "benched")
  return(rbind(iv_exp, iv_base, iv_bench) %>% unique() %>% dplyr::select(nature, everything()) %>% 
           filter(term == "treat") %>% mutate(iv_var = iv_var, control = controls))
}

iv_estimator(df_exp = nsw_dehejia_wahba, df_base = psid_controls_dw,
             treatment = 'treat', outcome = 're78')
```

### Matching

Now going to try a few different matching-based estimators.

#### Balance function

```{r}

library(MatchIt)
library(car)
library(lmtest)

### standard exact matching 
### figure out the best way to let users pass params into this
### eg Mahal dist

# ok to force outcome to be the same
# change this to make the treatment the same as default; update with status
bal_match <- function(df_exp, treat_exp, df_bench, treat_bench, 
                            outcome, match_meth, balance_vars, ...) {
 
  ## make the df with bench control
  
  df_bench_for_use <<- rbind(
    (df_bench %>% filter(!!sym(treat_bench)==0) %>% 
       select(all_of(balance_vars))),
    (df_exp %>% filter(!!sym(treat_exp)==1) %>% 
       select(all_of(balance_vars)))
    )
  
  ### balance estimator
  
  ## testing
  if (match_meth == 'cem') {
    match_out_exp <<- matchit(treat ~ age + education + black + hispanic + married + re74 + re75,
                            data = nsw_dehejia_wahba,
                            method = match_meth)
    match_out_bench <<- matchit(treat ~ age + education + black + hispanic + married + re74 + re75,
                        data = df_bench_for_use,
                        method = match_meth)
    # print(match_meth)
  }
  else if (match_meth == 'exact') {
    match_out_exp <<- matchit(treat ~ age + education + black + hispanic + married + re74 + re75,
                            data = nsw_dehejia_wahba, estimand = 'ATT',
                            method = match_meth, distance = 'mahalanobis', exact = exact_list, replace = TRUE)
    match_out_bench <<- matchit(treat ~ age + education + black + hispanic + married + re74 + re75,
                            data = df_bench_for_use, estimand = 'ATT',
                            method = match_meth, distance = 'mahalanobis', exact = exact_list, replace = TRUE)
    # print(match_meth)
  }
  else if (match_meth == 'subclass') {
    match_out_exp <<- matchit(treat ~ age + education + black + hispanic + married + re74 + re75,
                            data = nsw_dehejia_wahba, estimand = 'ATT',
                            method = match_meth, subclass = 5)
    match_out_bench <<- matchit(treat ~ age + education + black + hispanic + married + re74 + re75,
                            data = df_bench_for_use, estimand = 'ATT',
                            method = match_meth, subclass = 5) # relax this for user input later
  }
  
  else {
    print("You didn't give me a matching method I'm familiar with. Please select cem, exact, or subclass.")
  }
    
  
  ## is there a way to run various things using MatchIt object and save them to a new 'exact_bal_estimate' object'?
  ## eg:
  
  
  ## preparing the plots
  bal_plot_exp <- plot(summary(match_out_exp), var.order = 'unmatched')
  bal_plot_bench <- plot(summary(match_out_bench), var.order = 'unmatched')
  ## preparing the tables
  bal_table_exp <- 
    as.data.frame(summary(match_out_exp)[4]) %>% # and then probably kable this df, and output as ASCII or w.e
    mutate(data = 'experimental')
  bal_table_bench <- 
    as.data.frame(summary(match_out_bench)[4]) %>% 
    mutate(data = 'observational_benchmark')
  
  ## outputs
  plots <<- list(bal_plot_exp, bal_plot_bench)
  bal_tables <<- rbind(bal_table_exp, bal_table_bench)
  # didn't seem to stick on global out, but OK on `return`:
  # names(bal_tables) <- c('matched_means_treated', 'matched_means_control', 'matched_diff_means',
  #                        'matched_variance_ratio', 'matched_eCDF_mean', 'matched_eCDF_max',
  #                        'matched_std_pair_dist', 'data_source')
  # return(plots)
  # return(bal_tables)
  
  ## QUESTION: Do we want to allow users to compare balance between different samples?
}

## probably want to do something like ask users to pass a list of balance variables [DONE!]
balance_list <- c('treat', 're78','age','education', 'black', 'hispanic', 'married',
                're74', 're75'
                # 'u74', 'u75' # not in this version of the data
                )
# exact_var_list <- c('age', 'education', 'black', 'hispanic', 'married')
exact_def <- ~black + hisp + married + re74 + re75

# cem
bal_estim(df_exp = nsw_dehejia_wahba, treat_exp = 'treat',
                df_bench = psid_controls_dw, treat_bench = 'treat',
                outcome = 're78', match_meth = 'cem', balance_vars = balance_list)

  # mahalonbis + exact (for plots)
bal_estim(df_exp = nsw_dehejia_wahba, treat_exp = 'treat',
                df_bench = psid_controls_dw, treat_bench = 'treat',
                outcome = 're78', balance_vars = balance_list,
                match_meth = 'exact', exact_list = exact_def) # exact_list = exact_var_list

# bal_estim(df_exp = nsw_dehejia_wahba, treat_exp = 'treat',
#                 df_bench = psid_controls_dw, treat_bench = 'treat',
#                 outcome = 're78', match_meth = 'nearest')

```

#### Estimator function

Writing a function for estimating on matched / `matchit` objects.

```{r}

bal_estim <- function(match_objects, estim_meth, formula, ...) {
  ## want to let users pass a vector of match objects
  ## for lm, estimation formula should be passed from outside (no need to specify)
  
  if (estim_meth == 'logit' | estim_meth == 'glm') {
    att_list <- list()
    att_summary_obj_list <- list()
    for (m in match_objects) {
      att = glm(data = match, formula = lm_estim, weights = weights)
      att_summary_obj = lmtest::coeftest(att, vcov = vcovHC(att, type = "HC2")) # user can use add'l arguments to specify SE type
      att_list <- append(att_list, att) # is it better to `return` this?
      att_summary_obj_list <- append(att_summary_obj_list, att_summary_obj)
    }
    att_list <<- att_list
    att_summary_obj_list <<- att_summary_obj_list
    print('Your list of ATTs is called', substitute(att_list))
    print('Your list of ATT summary objects (w/ SEs) is called', substitute(att_summary_obj_list))
    # return() # i think the above setup is good
  }
  
  if (estim_meth == 'lm') {
    att_list <- list()
    # att_summary_obj_list_rob = list()
    att_summary_obj_list = list()
    
    att = (as.data.frame(lm(data = match.data(m), formula = lm_estim, weights = m$weights)[1])[2,]) # fix this...
    att_summary_obj = summary(att)
    # att_summary_obj_rob = lmtest::coeftest(att, vcov = vcovHC(att, type = "HC2"))
    att_list <- append(att_list, att)
    # att_summary_obj_list_rob = append(att_summary_obj_list_rob, att_summary_obj_rob)
    att_summary_obj_list = append(att_summary_obj_list, att_summary_obj)
    
    return(att_list)
    # return(att_summary_obj_list_rob)
    return(att_summary_obj_list)
  
    print('Your list of ATTs is called', substitute(att_list))
    print('Your list of ATT summary objects (w/ SEs) is called', substitute(att_summary_obj_list))
    
  }
}


```{r}
#####################################
# holding place for some of the old versions of the estimators
#####################################

### this script is to queue up some basic estimators for use in the package

# first...

# let's just start with DIM
# we can do something like a function that allows for a single estimator to be
# passed to two dataframes (or vice versa)

naive_dim_comparison <- function(df1, df2, treatment, outcome) {
  # initialize a df for final output
  final_output <<- as.data.frame(matrix())
  treatment_sym <- sym(treatment)
  outcome_sym <- sym(outcome)
  dim_estimator_df1 <- df1 %>%
    group_by(!!treatment_sym) %>%
    summarise(avg_earnings = mean(!!outcome_sym),
              earnings_var = var(!!outcome_sym),
              count = n())

  # need to input treatment_length fxn here
  # need to input control_length fxn here

  dim_estimate1 <<- dim_estimator_df1$avg_earnings[2] - dim_estimator_df1$avg_earnings[1]
  # see above for how to fix se
  # se_dim <<- sqrt((dim_estimator_df1[1,3]/length(df1$!!treatment_sym[df1$!!treatment_sym == 1])) +
  #                   (dim_estimator_df1[2,3]/length(df1$!!treatment_sym[df1$!!treatment_sym == 0])))

  # create the df of treatment-only from df1
  df1_treated_only <- df1 %>%
    filter(treat == 1) %>%
    # select(c(treatment, outcome))
    select(c('treat', 're78'))

  # create df2 and bind treatment-only from df1 to it
  dim_estimator_df2 <- df2 %>%
    # filter(!is.na(!!treatment_sym) & !is.na(!!outcome_sym)) %>%
    # select(c(!!treatment_sym, !!outcome_sym)) %>%
    select(c('treat', 're78')) %>%
    rbind(df1_treated_only) %>%
    group_by(!!treatment_sym) %>%
    summarise(avg_earnings = mean(!!outcome_sym, na.rm = TRUE),
              earnings_var = var(!!outcome_sym, na.rm = TRUE),
              count = n())

  # need to input treatment_length fxn here
  # need to input control_length fxn here

  dim_estimate2 <<- dim_estimator_df2$avg_earnings[2] - dim_estimator_df2$avg_earnings[1]

}

## Bug fixed to improve generalisability 
naive_dim_comparison <- function(df1, df2, treatment, outcome) {
  # Initialise relevant packages
  require(tidyverse)
  options(dplyr.summarise.inform = F)
  
  # Set up the treatment and outcome variables
  treatment_sym <- sym(treatment)
  outcome_sym <- sym(outcome)
  df1 <- df1 %>% mutate_at(treatment, as.numeric)
  df2 <- df2 %>% mutate_at(treatment, as.numeric)
  
  # Estimating the means and variances
  dim_estimator_df1 <- df1 %>%
    group_by(!!treatment_sym) %>%
    summarise(avg_earnings = mean(!!outcome_sym),
              earnings_var = var(!!outcome_sym),
              count = n())
  
  # Calculating the DIM estimates and SE
  dim_estimate1 <- filter(dim_estimator_df1, !!treatment_sym == 1)$avg_earnings - filter(dim_estimator_df1, !!treatment_sym == 0)$avg_earnings
  se_dim1 <- dim_estimator_df1 %>% mutate(se_cal = earnings_var / count) %>% colSums()
  se_dim1 <- se_dim1["se_cal"] %>% sqrt() %>% as.numeric()
  
  # Create the df of treatment-only from df1
  df1_treated_only <- df1 %>%
    filter(!!treatment_sym == 1 | !!treatment_sym == T) %>%
    dplyr::select(matches(paste(treatment, outcome, sep = "|")))

  # Create df2 and bind treatment-only from df1 to it
  dim_estimator_df2 <- df2 %>%
    drop_na(!!treatment_sym) %>% drop_na(!!outcome_sym) %>%
    dplyr::select(matches(paste(treatment, outcome, sep = "|"))) %>%
    rbind(df1_treated_only) %>%
    group_by(!!treatment_sym) %>%
    summarise(avg_earnings = mean(!!outcome_sym, na.rm = TRUE),
              earnings_var = var(!!outcome_sym, na.rm = TRUE),
              count = n())
  
  # Calculating the DIM estimates and SE
  dim_estimate2 <- filter(dim_estimator_df2, !!treatment_sym == 1)$avg_earnings - filter(dim_estimator_df2, !!treatment_sym == 0)$avg_earnings
  se_dim2 <- dim_estimator_df2 %>% mutate(se_cal = earnings_var / count) %>% colSums()
  se_dim2 <- se_dim2["se_cal"] %>% sqrt() %>% as.numeric()
  
  # Combining the outputs
  final_output <- c(dim_estimate1, se_dim1, dim_estimate2, se_dim2)
  names(final_output) <- c("dim_estimate1", "se_dim1", "dim_estimate2", "se_dim2")
  
  return(final_output)
}

data("lalonde")
naive_dim_comparison(lalonde, lalonde, "treat", "re78")
naive_dim_comparison(causaldata::Mroz, causaldata::Mroz, "lfp", "inc")
```


## Sandboxing

Trying a few things out:

```{r}

### trying to go from matchit objects to estimates (w/ summaries, etc.)

match_out_exp <<- matchit(treat ~ age + education + black + hispanic + married + re74 + re75,
                            data = nsw_dehejia_wahba, estimand = 'ATT',
                            method = 'subclass', subclass = 5)
match_out_bench <<- matchit(treat ~ age + education + black + hispanic + married + re74 + re75,
                            data = df_bench_for_use, estimand = 'ATT',
                            method = 'subclass', subclass = 5) # relax this for user input later

plot(match_out_exp, type = 'hist')

## now try the function

# create vector of matchit objects
match_objects_list <- list(match_out_bench, match_out_exp)

# broken: 
bal_estim(match_objects_list, estim_meth = 'lm', formula = lm_estim)

## patching

for (m in match_objects_list) {
  # print(substitute(m))
  # print(head(match.data(m)))
  # print(mean(m$subclass, na.rm = TRUE))
  
  att_list <- list()
  # att_summary_obj_list_rob = list()
  att_summary_obj_list = list()
  att = (as.data.frame(lm(data = match.data(m), formula = lm_estim, weights = m$weights)[1])[2,]) # fix this...
  att_summary_obj = summary(att)
  # att_summary_obj_rob = lmtest::coeftest(att, vcov = vcovHC(att, type = "HC2"))
  att_list <- append(att_list, att)
  # att_summary_obj_list_rob = append(att_summary_obj_list_rob, att_summary_obj_rob)
  att_summary_obj_list = append(att_summary_obj_list, att_summary_obj)
  
}



```


```{r}

### getting estimates out of the matched data

## define an lm to use throughout:

lm_estim <- re78 ~ treat + age + education + black + hispanic + married + re74 + re75

## estimation using subclass:

# matching
bal_estim(df_exp = nsw_dehejia_wahba, treat_exp = 'treat',
                df_bench = psid_controls_dw, treat_bench = 'treat',
                outcome = 're78', balance_vars = balance_list,
                match_meth = 'subclass' #, subclass_arg = 5 # relax for user input later 
                )


match_out_bench
match_out_exp

head(match.data(match_out_bench))
head(match.data(match_out_exp))

summary(match_out_bench$weights)
summary(match_out_exp$weights)

# inspection

plot(match_out_exp, 
     # type = "hist"
     type = "qq"
     )
plot(match_out_bench, type = "hist")

# estimation
att_subclass <- lm(data = match.data(match_out_exp),
                   formula = lm_estim,
                   weights = weights)

lmtest::coeftest(att_subclass, vcoc = vcovHC(att_subclass, type = "HC2"))


```






